Compositional Certified Resource Bounds\ifshort{\vspace{-1.15cm}}{}

### 2014-11-13 paper/main.tex
citing the coin-or website
spacing

We then feed the collected constraints to an
off-the-shelf LP solver (currently Coin-Or's CLP).
If the solver successfully finds a solution, we know that a derivation
exists and extract the values for the initial
$Q$ from the solver to get a resource bound for the program.  To get
a full derivation we extract the complete solution from the
solver, and apply it to the symbolic names $q_i$ of the coefficients
in the derivation.  If the LP solver fails to find a solution, an
error is reported.

@@

When the resource bound of a program depends on the contents of the
heap, or is non-linear (e.g. logarithmic, exponential), we propose to
introduce a \emph{logical state} using \emph{auxiliary variables}.
Auxiliary variables guide $\toolname$ during bound derivation
but they do not change the behavior of the program.

@@

\begin{figure}[t]
\center
\vspace{-.2cm}
\includegraphics[width=.9\linewidth]{fig/bound3d}
\caption{The automatically derived bound $1.33|[x,y]| + 0.33 |[0,x]|$
  (blue lines) and the measured runtime cost (red crosses) for Example
  \emph{t08}. For $x\ge 0$ the bound is tight.}
\label{fig:3d}
\end{figure}

>>>>

We then feed the collected constraints to an
off-the-shelf LP solver (currently CLP~\cite{clp}).
If the solver successfully finds a solution, we know that a derivation
exists and extract the values for the initial
$Q$ from the solver to get a resource bound for the program.  To get
a full derivation we extract the complete solution from the
solver, and apply it to the symbolic names $q_i$ of the coefficients
in the derivation.  If the LP solver fails to find a solution, an
error is reported.

@@

When the resource bound of a program depends on the contents of the
heap, or is non-linear (e.g. logarithmic, exponential), we
introduce a \emph{logical state} using \emph{auxiliary variables}.
Auxiliary variables guide $\toolname$ during bound derivation
but they do not change the behavior of the program.

@@

\begin{figure}[t]
\center
% \vspace{-.2cm}
\includegraphics[width=.9\linewidth]{fig/bound3d}
\caption{The automatically derived bound $1.33|[x,y]| + 0.33 |[0,x]|$
  (blue lines) and the measured runtime cost (red crosses) for Example
  \emph{t08}. For $x\ge 0$ the bound is tight.}
\label{fig:3d}
\end{figure}
